### 2018-05-06 msc_diploma_cubesat_galgoczi.tex
text

\vspace{1 cm}
\begin{large}\textbf{Detailed feasibility study of a gamma ray detector system for nanosatellites using GEANT4 simulations}\end{large}\\
\vspace{1 cm}
%\begin{larger}\textbf{BSc szakdolgozat}\\ \end{larger}
%\vspace{0.5 cm}
\textit{\textbf{Galgóczi Gábor$^{*}$, Fizikus MSc szak, 2. évfolyam}}\\
Eötvös Loránd Tudományegyetem, Természettudományi Kar\\
WIGNER Fizikai Kutatóközpont - MTA\\
\vspace{1.5cm}
\begin{figure}[H]
\centering
\begin{tabular}{ >{\centering\arraybackslash}m{2in}  >{\centering\arraybackslash}m{2.5in}  }

\includegraphics[width=53.0mm]{images/regard.jpg}
\end{tabular}
\end{figure}

\begin{figure}[H]
\centering
\begin{tabular}{ >{\centering\arraybackslash}m{2in}  >{\centering\arraybackslash}m{2.5in}  }

\includegraphics[width=45.0mm]{images/elte.png} \parbox{0pt}{\rule{0pt}{2ex+\baselineskip}} &
\hspace{0.2 cm}
\includegraphics[width=40.0mm]{images/wigner.png}
\end{tabular}
\end{figure}

@@

\vspace{0.1 cm}
\end{center}

\begin{center}
\begin{tabular}{ll}
\centerline{ Témavezetők: } \\
\centerline{ Conseil Européen pour la Recherche Nucléaire (CERN)}
\end{tabular}
\end{center}
\begin{center}

\vspace{2.5 cm}
\large \textbf {2016}\\
\end{center}
\end{titlepage}
%\doublespacing
\tableofcontents
%\singlespacing
\pagenumbering{roman}

@@

\subsection{2 channel setup}

\includegraphics[width=100.0mm]{images/2channel.png}

@@

\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
ANT		&  110		& Stainless Steel 	& 50\\
		&  & FR4 Glass-Epoxy sheet	& 50\\\hline
AUX		& 100	& 	FR4 Glass-Epoxy sheet	& 100\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	1100	& 	As you wish	& 	100\\
 \hline
\end{tabular}
\end{center}

@@

Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline					
Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline

 \hline
\end{tabular}
\end{center}

@@

\includegraphics[width=100.0mm]{images/irradiation.png}

\includegraphics[width=40.0mm]{images/positions.png}

@@

\subsection{Simulation of background in space}

\subsection{Optimalization of the scintillator detectors}
\section{Conclusion}

>>>>

\vspace{1 cm}
\begin{large}\textbf{Detailed feasibility study of a gamma ray detector system for nanosatellites using GEANT4 simulations}\end{large}\\
\vspace{1 cm}
%\begin{larger}\textbf{BSc szakdolgozat}\\ \end{larger}
%\vspace{0.5 cm}
\textit{\textbf{Galgóczi Gábor$^{*}$, Fizikus MSc szak, 2. évfolyam}}\\
Eötvös Loránd Tudományegyetem, Természettudományi Kar\\
WIGNER Fizikai Kutatóközpont - MTA\\
\vspace{1.5cm}

\begin{figure}[H]
\centering

\includegraphics[width=80.0mm]{images/elte.png}  
\end{figure}

@@

\vspace{4 cm}
\end{center}

\begin{center}
\begin{tabular}{ll}
\centerline{ Témavezetők: } \\
\centerline{ Norbert Werner (ELTE)}
\end{tabular}
\end{center}
\begin{center}

\vspace{2.5 cm}
\large \textbf {2018}\\
\end{center}
\end{titlepage}
%\doublespacing
\tableofcontents
%\singlespacing
\pagenumbering{roman}

@@

\includegraphics[width=150.0mm]{images/irradiation.png}

\subsection{2 channel read out setup}

\begin{figure}[H]
\includegraphics[width=160.0mm]{images/2channel.png}
\caption{Simulation of 100 $\gamma$s emitted from the source. The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation. Only the photons that were detected are drawn.}
\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
ANT		&  110		& Stainless Steel 	& 50\\
		&  & FR4 Glass-Epoxy sheet	& 50\\\hline
AUX		& 100	& 	FR4 Glass-Epoxy sheet	& 100\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	1100	& 	As you wish	& 	100\\
 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite}
\end{table}

\begin{table}

@@

Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline					
Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline
\end{tabular}
\end{center}
\caption{The chemical composition of materials that are used for the satellite}
\end{table}

@@

\includegraphics[width=80.0mm]{images/positions.png}

@@

\subsection{Simulation of the cosmic background in space}

\subsection{Optimalization of the scintillator detectors}

\pagebreak
\section{Conclusion}

In order to simulate how the XXX CubeSat would interact with the cosmic background and how sensitive it would be to the GRBs that it is designed to investigate a Geant4 simulation was built.

As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the particle detector of the satellite -- was implemented in Geant4. The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs that was used to read out the scintillator.

Secondly, the CAD model of the satellite was exported to Geant4. The body of the satellite was divided into 8 modules. The chemical components of these modules were included in the simulation. The scintillator was placed on the side of the satellite.

Thirdly, the effect of cosmic radiation was invastigated by obtaining the energy spectra of cosmic protons and electrons at the XXX altitude of XXX. The satellite was radiated by these particles in Geant4 from all directions to investigate how large the signal of these particles would be. This needs to be minimalized as it versenyez with the signal of gamma particles from GRBs.

Finally, the $\gamma$ absorption of the satellite was invastigated.
